Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-04 paper.qmd
Added images on the tSNE layout (MNIST)

# # read the png file from device 
# left_top_img <- readPNG("figures/mnist/mnist_digit1_img_lt.png", native = TRUE)
# center_img <- readPNG("figures/mnist/mnist_digit1_img_c.png", native = TRUE)
# right_bottom_img <- readPNG("figures/mnist/mnist_digit1_img_rb.png", native = TRUE)
# 
# tsne_plot_mnist <- tsne_plot_mnist +
#     inset_element(p = left_top_img, 
#                   left = 0.8, 
#                   bottom = 0.85, 
#                   right = 0, 
#                   top = 0.95) +
#     inset_element(p = center_img, 
#                   left = 1.2, 
#                   bottom = 0.6, 
#                   right = 0, 
#                   top = 0.7) +
#     inset_element(p = right_bottom_img, 
#                   left = 1.7, 
#                   bottom = 0.48, 
#                   right = 0, 
#                   top = 0.58)
```

>>>>

# read the png file from device
left_top_img <- readPNG("figures/mnist/mnist_right_top_img.png", native = TRUE)
center_img <- readPNG("figures/mnist/mnist_middle_img.png", native = TRUE)
right_bottom_img <- readPNG("figures/mnist/mnist_right_bottom_img.png", native = TRUE)

tsne_plot_mnist <- tsne_plot_mnist +
    inset_element(p = left_top_img,
                  left = 1,
                  bottom = 0.85,
                  right = 0,
                  top = 0.95) +
    inset_element(p = center_img,
                  left = 0.8,
                  bottom = 0.5,
                  right = 0,
                  top = 0.6) +
    inset_element(p = right_bottom_img,
                  left = 1,
                  bottom = 0.2,
                  right = 0,
                  top = 0.3)
```
